### 2025-02-22 manuscript/_figure4.qmd
Fixed Fig 4 id and x label. Added missing references and moved table 4 caption.

```{r}
#| label: fig3
#| fig-width: 16
#| fig-height: 6
#| echo: false
#| fig.cap: > 
#|   Forest (A) and funnel (B) plots of the best classification models from all MER studies.

@@

fp1 <- grid.grabExpr(print(data |>
  forestplot(labeltext = c(study, n, cor),
             xlab = "Correlation",
             xticks = c(0, .25,.5,.75, 1),
             clip = c(0, 1))|>
    fp_add_header(study = "Study",n = "N",cor = expression(italic(r))) |>
    fp_append_row(mean  = FisherZInv(m.cor$TE.random),
                lower = FisherZInv(m.cor$lower.random),
                upper = FisherZInv(m.cor$upper.random),
                study = "Summary",
                n = sum(m.cor$n),
                cor = round(FisherZInv(m.cor$TE.random),3),
                is.summary = TRUE) |>
  fp_set_style(box = "grey50",
               line = "grey20",
               summary = "black",
                txt_gp = fpTxtGp(label = list(gpar(cex = 0.80)),
                                ticks = gpar(cex = 0.80),
                                xlab  = gpar(cex = 0.80)))|>
    fp_decorate_graph(grid = structure(FisherZInv(m.cor$TE.random),gp = gpar(lty = 2, col = "grey30")))
)
)

#### Funnel plot using a custom function
source('../etc/custom_funnel_plot.R')
fp2 <- suppressWarnings(custom_funnel_plot(m.cor))

>>>>

```{r}
#| label: fig4
#| fig-width: 16
#| fig-height: 6
#| echo: false
#| fig.cap: > 
#|   Forest (A) and funnel (B) plots of the best classification models from all MER studies.

@@

fp1 <- grid.grabExpr(print(data |>
  forestplot(labeltext = c(study, n, cor),
             xlab = "Matthews Correlation Coefficient",
             xticks = c(0, .25,.5,.75, 1),
             clip = c(0, 1))|>
    fp_add_header(study = "Study",n = "N",cor = expression(italic(r))) |>
    fp_append_row(mean  = FisherZInv(m.cor$TE.random),
                lower = FisherZInv(m.cor$lower.random),
                upper = FisherZInv(m.cor$upper.random),
                study = "Summary",
                n = sum(m.cor$n),
                cor = round(FisherZInv(m.cor$TE.random),3),
                is.summary = TRUE) |>
  fp_set_style(box = "grey50",
               line = "grey20",
               summary = "black",
                txt_gp = fpTxtGp(label = list(gpar(cex = 0.80)),
                                ticks = gpar(cex = 0.80),
                                xlab  = gpar(cex = 0.80)))|>
    fp_decorate_graph(grid = structure(FisherZInv(m.cor$TE.random),gp = gpar(lty = 2, col = "grey30")))
)
)

#### Funnel plot using a custom function
source('../etc/custom_funnel_plot.R')
fp2 <- suppressWarnings(custom_funnel_plot(m.cor, metric = "MCC"))

### 2025-02-22 manuscript/manuscript.qmd
Fixed Fig 4 id and x label. Added missing references and moved table 4 caption.

Accounting for outliers among the classifications results removes 6 studie, affecting both performance ($MCC$ = 0.8941, 95%CI: 0.8282-0.9356) and heterogeneity scores ($\tau^2$ = 0.0569, $I^2$ = 97.7%). However, Eggers' test does not indicate an asymmetric funnel plot ($\beta$ = -19.769, 95%CI: -39.29--0.24). After aggregating across dimensions, some of the best models included only classified arousal (@zhang2016; @zhang2017). To assess these studies' impact on overall performance, we conducted the same meta-analytic procedure after excluding them. Classification accuracy ($MCC$ = 0.8758, 95%CI: 0.7235-0.9468) does not change notably, nor does the rank order of model classes in terms of performance. Conseqeuntly, we report on all 12 in subsequent analyses.

@@

<!-- | All Trim | 29,6499     | 0.8185 \[0.8046; 0.8314\] | 58.3 | 0.0001 | 0.0066   | 60.4% | -->

<!-- | Max Trim | 6,3653      | 0.8689 \[0.7760; 0.9249\] | 11.6 | 0.0001 | 0.0749   | 97.5% | -->

@@

Figure 3. Forest plot of arousal prediction (Max?) (Unless we do some custom plotting)

-   Figure Optional: Funnel plot (I haven't seen this yet)

>>>>

Accounting for outliers among the classifications results removes 6 studie, affecting both performance ($MCC$ = 0.8941, 95%CI: 0.8282-0.9356) and heterogeneity scores ($\tau^2$ = 0.0569, $I^2$ = 97.7%). However, Eggers' test does not indicate an asymmetric funnel plot ($\beta$ = -19.769, 95%CI: -39.29--0.24). After aggregating across dimensions, some of the best models included only classified arousal (@zhang2016br; @zhang2017fe). To assess these studies' impact on overall performance, we conducted the same meta-analytic procedure after excluding them. Classification accuracy ($MCC$ = 0.8758, 95%CI: 0.7235-0.9468) does not change notably, nor does the rank order of model classes in terms of performance. Conseqeuntly, we report on all 12 in subsequent analyses.

@@

@@
